Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
gg

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   set.seed(456)
   b <- connect.caves(c = 4, nc = 4, n = 24)
   gg2 <- function(x, lay.o = "kk") {
      n <- vcount(x)
      V(x)$name <- 1:n
      d <- distinction(x)[, 3]
      c <-  vector(mode = "character", length = length(d))
      c[which(d < -0.05)] <- "tan2"
      c[which(d > 0.05)] <- "blue"
      c[which(d >=-0.05 & d <= 0.05)] <- "purple"
      c[which(d == max(d))] <- "red"
      w <- ggraph(x, layout = lay.o) + 
      geom_edge_link(color = "steelblue") + theme_graph() +
      geom_node_point(size = 5, color = c) + 
      geom_node_text(aes(label = name), color = "white", size = 3) 
      return(w)
      }
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:4)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples1.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(5:8)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples2.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(9:12)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples3.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(13:16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples4.png"), width = 10, height = 10, units = "in")
```

>>>>

## Connected Caves Computational Experiments
```{r}
   source(here("Functions", "connect.caves.R"))
   source(here("Functions", "gg2.R"))
   set.seed(456)
   b <- connect.caves(c = 4, nc = 4, n = 24)
   p.list <- lapply(b, gg2, lay.o = "auto")
   for (i in 1:length(p.list)) {
      p.list[[i]] <- p.list[[i]] + ggtitle(paste("N. Long Ties =", i-1)) +
         theme(plot.title = element_text(size = 11))
      }
   wrap_plots(p.list[c(1:4)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples1.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(5:8)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples2.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(9:12)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples3.png"), width = 10, height = 10, units = "in")
   wrap_plots(p.list[c(13:16)], nrow = 2)
   ggsave(here("Plots", "connected-caves-examples4.png"), width = 10, height = 10, units = "in")
```
